Environmental behaviour & practices

### 2021-04-12 03-Sustainable-behaviour.Rmd
presentation

  - first_name: "Mauricio"
    last_name: "Camargo"
    url: https://erpi.univ-lorraine.fr/people/Mauricio-Camargo/
    affiliation: ERPI
    affiliation_url: https://erpi.univ-lorraine.fr/
    orcid_id: 0000-0003-3867-2438

---
```{r, include=FALSE}
require(DiagrammeR)
require(tidyverse)
require(kableExtra)
require(widgetframe)
```

>>>>

  - first_name: "Mauricio"
    last_name: "Camargo"
    url: https://erpi.univ-lorraine.fr/people/Mauricio-Camargo/
    affiliation: ERPI
    affiliation_url: https://erpi.univ-lorraine.fr/
    orcid_id: 0000-0003-3867-2438 
always_allow_html: true        
---
```{r, include=FALSE}
require(DiagrammeR)
require(tidyverse)
require(kableExtra)
require(widgetframe)
```

```{r, include=FALSE}

#library(rticles)
#library(rmarkdown)
#render("03-Sustainable-behaviour.Rmd", output_format = "word_document", output_dir = "03-Sustainable-behaviour")

#render("01-Sustainable-indicators.Rmd", output_format = "pdf_document", output_dir = "01-Sustainable-Indicators")
#render("01-Sustainable-indicators.Rmd", output_format = "elsevier_article", output_dir = "01-Sustainable-Indicators")

```
